FoRTE baseline

### 2019-09-18 analysis/paper/paper.Rmd
Suggestions for first part of discussion

Our first question was: To what extent can the model, under any configuration, reproduce the observed reality?
**Ensemble mean trajectory matches traditional understanding of succession**---rapid growth to peak productivity, followed by gradual decline [@odum_1969_strategy_ecosystem_development]---but **happens too quickly** (Figure 2);
real ecosystems sustain peak productivity for longer [@gough_2016_disturbance].
This idea that ED2.2's main issue is that it is moving too quickly is supported by the fact that ED2.2 generally underestimates productivity after 100 years, but model **predictions at peak productivity are close to reality**.
One reason ED2.2 is moving too quickly through succession is **missing mechanisms for sustaining productivity through early succession**.
In particular, recent evidence points to the **important role of low-severity, high-frequency disturbances** in sustaining ecosystem productivity [@gough_2016_disturbance].
ED2.2 has a mortality scheme, and indeed, parameters related to mortality were often among the top 10 most important parameters for predictive uncertainty (Figure 6).
<!-- Maybe move this elsewhere? -->
<!-- TODO Look at mortality across ED runs. Does it relate at all to results? -->
However, **our simulations did not include other sources of disturbance**, such as partial harvests, extreme weather, and damage from insects and pathogens, which are common to this region [@amiro_2010_ecosystem] and which may contribute to sustaining productivity and dominance of early-successional forests [@gough_2016_disturbance].
Future work will: (1) Calibrate ED2.2 disturbance response to experimental observations (FoRTE), and (2) run long-term simulations with prescribed disturbance frequencies and see how they affect ecological dynamics.

>>>>

Our first question was: To what extent can the model, under any configuration, reproduce the observed reality?
**Ensemble mean trajectory matches traditional understanding of succession**---rapid growth to peak productivity, followed by gradual decline [@odum_1969_strategy_ecosystem_development]---but **happens too quickly** (Figure 2);
real ecosystems sustain peak productivity for longer [@gough_2016_disturbance]. 
This is a common characteristic of many ecosystem models: they may be relatively insensitive to short-term changes (e.g. https://onlinelibrary.wiley.com/doi/full/10.1111/gcb.13626) but have trouble sustaining forest production over long time periods, not capturing forest resilience (https://www.sciencedirect.com/science/article/pii/S0378112716310581). 
This is likely because of species successional changes (https://www.nature.com/articles/s41598-018-23763-y, https://www.mdpi.com/1999-4907/9/8/460) and the role of minor or subtle disturbances (http://dx.doi.org/10.1111/nph.15227). 
Neither of these processes is well captured by current models (https://onlinelibrary.wiley.com/doi/full/10.1111/j.1365-2486.2004.00891.x, maybe B-L 2016?). 
This is likely to be an increasingly important limitation in a world of rising disturbances and climate-driven species changes.

This idea that ED2.2's main issue is that it is moving too quickly is supported by the fact that ED2.2 generally underestimates productivity after 100 years, but model **predictions at peak productivity are close to reality**. (https://onlinelibrary.wiley.com/doi/full/10.1111/gcb.13077) 
One reason ED2.2 is moving too quickly through succession is **missing mechanisms for sustaining productivity through early succession**.
In particular, recent evidence points to the **important role of low-severity, high-frequency disturbances** in sustaining ecosystem productivity [@gough_2016_disturbance].
ED2.2 has a mortality scheme, and indeed, parameters related to mortality were often among the top 10 most important parameters for predictive uncertainty (Figure 6). 
In addition, **our simulations did not include other sources of disturbance**, such as partial harvests, extreme weather, and damage from insects and pathogens, which are common to this region [@amiro_2010_ecosystem] and which may contribute to sustaining productivity and dominance of early-successional forests [@gough_2016_disturbance]. 
We suggest that how these mortality processes interact with factors such as canopy restructuring and thus radiation transmission (http://dx.doi.org/10.1016/j.foreco.2013.02.031), sustaining the productivity of aging forests over decades (Luyssaert 2008?) is critical to explore in future research.

Future work will: (1) Calibrate ED2.2 disturbance response to experimental observations (FoRTE), and (2) run long-term simulations with prescribed disturbance frequencies and see how they affect ecological dynamics.
